Library of Actions: Implementing a Generic Robot Execution Framework by Using Manipulation Action Semantics

### 2015-01-05 paper_new.tex
method is changed

\begin{figure}[hb]
      \centering
      \includegraphics[scale=0.5]{./pdf/Figure_PerceptionAction.pdf}
      \caption{ Perception-action Chain}
      \label{fig:action_graph_sec}
\end{figure}

@@

Before describing the complete framework in detail, we will briefly provide an overview of each algorithmic step illustrated in Fig.~\ref{fig:block_diagram}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Low-level primitives}
\label{section_primitives}
In section.\ref{sec:abstract_primitives} we defined the primitives which are performed by the manipulator.
Here we describe our implementation of these primitives at the low-level.

>>>>

\begin{figure}[hb]
      \centering
      \includegraphics[scale=0.5]{./pdf/Figure_PerceptionAction.pdf}
      \caption{ Perception-action Chain}
      \label{fig:per_act_cycle}
\end{figure}

@@

As illustrated in Fig.~\ref{fig:per_act_cycle} our proposed perception action chain involves three main components: {\it high-}, {\it mid-}, and {\it low-level} action units. In this section we will provide the detailed description of each component together with their sub-elements as depicted in Fig.~\ref{fig:block_diagram}.

\begin{itemize}
  \item[$\bullet$] The first item
  \item[$\bullet$] The second item
  \item[$\bullet$] The third etc \ldots
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Low-level primitives}
\label{section_primitives}
In section.\ref{sec:abstract_primitives} we defined the primitives which are performed by the manipulator.
Here we describe our implementation of these primitives at the low-level.
